RVD2: An ultra-sensitive variant detection model for heterogeneous population sequencing

### 2013-09-07 doc/bioinformatics2013/RVD2.tex
Paper draft update on result section ROC curve

\subsection{Sampling from $p \left( \theta_{ij} |r_{ij},n_{ij},\mu_j,M \right)$}

@@

\section{Results}
Figure 1 Overall of the process
\subsection{Simulation Results}
\subsection{Comparison Results on Synthetic DNA}
Figure 3 ROC comparison with other methods: varscan/samtools/rvd
\subsection{Empirical Results on Multiple Sclerosis Data}
We tested our method on sequence data from clinical Multiple Sclerosis samples. We expect to see that

Table: Table of Variants
\subsection{Performance with read depth}
Figure 4 ROC by read depth
picard to thin segment data, showing performance as read depth decreasing

>>>>

\subsection{Sampling from $p \left( \theta_{ij} |r_{ij},n_{ij},\mu_j,M \right)$}\

@@

\section{Results}

\subsection{Overall of the process}
Figure 1

\subsection{Performance with read depth}\
Figure 2 ROC plot showing performance with different read depth

picard to thin segment data, showing performance as read depth decreasing

\begin{figure}[h]
\begin{center}
%\includegraphics[width=160mm]{eps_figs/ROC_without_chi2.eps}
\caption{ROC curve varying read depth showing detection performance of model with Bayesian Hypothesis Test.}
\label{fig:ROC_without_chi2}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=160mm]{pdf_figs/ROC_without_chi2.pdf}
\caption{ROC curve varying read depth showing detection performance of model with Bayesian Hypothesis Test.}
\label{fig:ROC_without_chi2}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=160mm]{pdf_figs/MuBarPlot.pdf}
\caption{ROC curve varying read depth showing detection performance of model with Bayesian Hypothesis Test.}
\label{fig:ROC_without_chi2}
\end{center}
\end{figure}

We tested the mutation detection power of our graphical model on synthetic dataset with dilution rates $0.1\%$, $0.3\%$, $1.0\%$, $10.0\%$ and read depth varying from $10^2$ to $10^5$.Different read depth dataset was achieve by thining dataset with read depth up to $10^6$ using Picard.The model had high detection power when the read depth was at $10^5$ level. At dilution rate at $0.1\%$, the model achieved performance with sensitivity at 99.74\% and specificity at 92.86\%. We missed one mutation at position 205 and had one false positive at position 8. The threshold was chosen at 0.022\% which achieved the optimal sensitivity and specificity in the ROC curve. As expected, the detection power of the graphical model decreased when the read depth was reduced.

\begin{figure}[h] %needs to go to supplementary document.
\begin{center}
\includegraphics[width=160mm]{pdf_figs/ROC_subplots_with_chi2.pdf}
\caption{ROC curve varying read depth showing method performance with Bayesian baHypothesis Testing and Chi-Square Test}
\label{fig:R}
\end{center}
\end{figure}
We also evaluateed the performance of the graphical model with Chi-square test included in the hypothesis testing.

Low read depth limited the False positive rate. we are confident in the callings

High read depth Not much influence. do not bring about bad influence

\subsection{Comparison Results on Synthetic DNA}\

Figure 3 ROC comparison with other methods: varscan/samtools/rvd

\subsection{Empirical Results on Multiple Sclerosis Data}\
We tested our method on sequence data from clinical Multiple Sclerosis samples. We expect to see that

Table: Table of Variants
